An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-05-05 poly-embed-journal/poly-embed-journal.tex
Updates in Section 5; added some descriptive text and touch up proof of Prop 6

\begin{definition}
  \raft{For Bo: added this def, changed def embedding}
  Let $L:\R\to\reals^\Y_+$ be a generic loss.
  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  We further say $\Sc$ is a \emph{minimum representative set}\jessiet{Propogate change} if it has the smallest cardinality among all representative sets.
\end{definition}

\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ \emph{over a set} $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

\begin{figure}
	\begin{minipage}{0.3\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{figs/0-1-br.pdf}
		\caption{Bayes Risk of the 0-1 loss.}
		\label{fig:0-1-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{figs/hinge-br.pdf}
		\caption{Bayes Risk of Hinge Loss.}
		\label{fig:hinge-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{figs/logistic-br.pdf}
	\caption{Bayes Risk of the logistic loss.}
	\label{fig:logistic-br}
\end{minipage}
\end{figure}

@@

    %\btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
  (For intuition, one can consider the relative interiors in $\reals^\Y_+$, but we need to consider interiors in order to apply previous results.)
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
  \raft{I believe we can remove mentions of power diagrams here; let's give it a try.  I don't think we need to project yet, given what we say next.}
  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$. \jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead. -21 Mar 21}

@@

\raf{Something like this:}\\
Together, Lemma~\ref{lem:loss-restrict} and Proposition~\ref{prop:embed-bayes-risks} give the following useful tool for finding embeddings.
\begin{corollary}\label{cor:representative-embeds-restriction}
  Let surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
  If a finite set $\U \subseteq \reals^d$ is representative for $L$, then $L$ embeds the discrete loss $L|_\U$.
\end{corollary}

@@

\raft{I wonder if we should demote this to a corollary.  We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.  Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.  I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  \proposedadd{Form the set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  
  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.}
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

@@

\begin{lemma}
	\label{lem:poly-loss-poly-risk}
	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
\end{lemma}
\begin{proof}
	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite.
	For each $U\in \U$, select $u_U \in U$, and let $\Sc' = \{u_U : U \in\U\}$.
	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
\end{proof}

@@

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
	Let $\R$ be a finite representative set for $L$ eliciting $\Gamma$.
	The following are equivalent:
	\begin{enumerate}
		\item[a.] $\R$ is a minimum representative set for $L$.
		\item[b.] $L|_\R$ is non-redundant.
		\item[c.] For all $r \in \R$, $\Gamma_r$ is full-dimensional and there is no $r' \in \R'$ such that $\Gamma_{r'}= \Gamma_r$, and $\cup_{r\in\R} \Gamma_r = \simplex$.
	\end{enumerate}
\end{proposition}
\begin{proof}[Sketch]
	$(a \implies b)$  
	We show the contrapositive: suppose $L|_\R$ is redundant.
	Then there is a $r,r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
	Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
	Therefore, $\R \setminus \{r\}$ still a representative set, so $\R$ is not minimum.

@@

	$(c \implies a)$
	As $\Gamma_r$ is full-dimensional and there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$, for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
	Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
	Therefore, $\R$ is minimum.
\end{proof}

\begin{corollary}
	If $\R$ is a minimum representative set for $L$, then $L$ tightly embeds $L|_\R$.
\end{corollary}
\jessie{Add text about how this lets us think about general targets}

\begin{proposition}
	Suppose $\R$ and $\R'$ are minimum representative sets for the loss $L$.
	Then $\{L(r) \mid r \in \R\} = \{L(r') \mid r' \in \R'\}$.
\end{proposition}
\begin{proof}[Sketch]
	It suffices to show $\{L(r) \mid r \in \R\} \subseteq \{L(r') \mid r' \in \R'\}$, and equality will follow by symmetry.
	Consider $r\in \R$, and we want to show $L(r) \in \{L(r') \mid r' \in \R'\}$.
	Since $\R$ and $\R'$ are minimum representative sets, all the level sets must be full-dimensional, and therefore have well-defined interiors (Proposition~\ref{prop:tfae-min-rep-nonredundant}).
	In particular, we must have $\Gamma_r = \Gamma_{r'}$ for some $r' \in \R'$.
	If $L(r) \neq L(r')$, then there would be a distribution $p \in \inter{\Gamma_r}$ such that $\inprod{p}{L(r)} \neq \inprod{p}{L(r')}$. \jessiet{This needs more detail}
	If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore not a representative set.
	Similarly, if the inequality were flipped, we would contradict $\R$ being a representative set.
	Therefore, we must have the losses equal, and $L(r) \in \{L(r') \mid r' \in \R'\}$.
\end{proof}

\begin{definition}[Trim]\label{def:trim-loss}
	Given a loss $L:\R \to \reals_+^\Y$, we define $\trim(L) = \{L(r) \mid r \in \R\}$ given any minimal representative set $\R$ for $L$.
\end{definition}

\begin{proposition}\label{prop:trim-loss-condition}
	Given an loss $L : \R \to \reals^\Y_+$, we have $\trim(L) = \{L(u) : u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\end{proposition}
\begin{proof}[Sketch]
	Suppose $L(u) \in \trim(L)$.
	By Proposition~\ref{prop:tfae-min-rep-nonredundant}, we know $\Gamma_u$ is a full-dimensional level set, and there exists a $p_u$ such that $\{u\} = \Gamma(p_u)$.
	Therefore, $\Gamma_u$ cannot be a subset of any other level set, so $L(u) \in \{L(u) \mid \neq \exists u' s.t. /, \Gamma_u \subsetneq \Gamma_{u'}\}$.

	Now, suppose $L(u) \in \{L(u) \mid \neq \exists u' s.t. /, \Gamma_u \subsetneq \Gamma_{u'}\}$.
	If $L(u) \not \in \trim(L)$, then there is a $u'$ so that $L(u') \in \trim(L)$ and $\Gamma_u \subseteq \Gamma_{u'}$.
	By the set construction, we must have $\Gamma_u = \Gamma_{u'}$, and since $\R$ is a minimum representative set, we know there is a $p_{u'}$ such that $\{u'\} = \Gamma(p_{u'})$.
	Therefore, we must have $u=u'$, so $L(u') = L(u) \in \trim(L)$.
\end{proof}

\begin{proposition}\label{prop:embed-iff-trims-equal}
	Let $\ell$ eliciting $\gamma$ be a discrete loss and $\R$ a minimum representative set for $\ell$.
	$L$ (eliciting $\Gamma$) embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
\end{proposition}
\begin{proof}[Sketch]
	$\implies$
	The optimality condition of embedding means $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R$.
	$\R$ a minimum representative set then implies $\varphi(\R)$ is a minimum representative set for $L$.
	Importantly, we have
	\begin{equation*}
	\trim(L) = \trim(L|_{\varphi(\R)}) = \trim(\ell|_\R) = \trim(\ell)~.~
	\end{equation*}
	The outside equalities follow from the sets being minimum representative sets, and the middle one follows from the embedding definition since losses have to match at embedded points.

	$\impliedby$
	First, take $\varphi: r \mapsto u$ if $\ell(r) = L(u)$.
	As these losses match we trivially have the second embedding condition matching losses.
	It just remains to show $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	\begin{align*}
	r \in \argmin_u \inprod{p}{\ell(u)} &\iff \ell(r) = \min_u \inprod{p}{\ell(u)}\\
	&\iff \ell(r) = \min_{u \in \R} \inprod{p}{\ell(u)} \\
	&\iff L(\varphi(r)) = \min_{u \in \varphi(\R)} \inprod{p}{L(u)} \\
    &\iff L(\varphi(r)) = \min_u \inprod{p}{L(u)} \\
    &\iff \varphi(r) \in \argmin_{u} \inprod{p}{L(u)}
	\end{align*}
\end{proof}

>>>>

\begin{definition}
  \raft{For Bo: added this def, changed def embedding}
  Let $L:\R\to\reals^\Y_+$ be a generic loss.
  We say $\Sc \subseteq \R$ is \emph{representative for $L$} if we have $\prop{L}(p) \cap \Sc \neq \emptyset$ for all $p\in \simplex$.
  We further say $\Sc$ is a \emph{minimum representative set}\jessiet{Propogate change} if it has the smallest cardinality among all representative sets.
\end{definition}
Minimum representative sets are essentially the same as \emph{maximally informative sets} from~\citet{wang2020weston}, but we found the name minimum representative set to give more intuition about being the smallest such set.

\begin{definition}[Embedding a loss]\label{def:loss-embed}
  A loss $L:\reals^d\to\reals^\Y$ \emph{embeds} a loss $\ell:\R\to\reals^\Y$ over a representative set $\Sc$ if there exists some injective embedding $\varphi:\Sc\to\reals^d$ such that
  (i) for all $r\in\Sc$ we have $L(\varphi(r)) = \ell(r)$, and (ii) for all $p\in\simplex,r\in\R$ we have
  % \begin{equation}\label{eq:embed-loss}
  %   r \in \argmin_{r'\in\R} \inprod{p}{\ell(r')} \iff \varphi(r) \in \argmin_{u\in\reals^d} \inprod{p}{L(u)}~.
  % \end{equation}
  \begin{equation}\label{eq:embed-loss}
    r \in \prop{\ell}(p) \iff \varphi(r) \in \prop{L}(p)~.
  \end{equation}
  We simply say $L$ \emph{embeds} $\ell$ if there is some representative set $\Sc$ for $\ell$ such that $L$ embeds $\ell$ over $\Sc$.
\end{definition}

@@

\begin{figure}
	\begin{minipage}{0.3\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{figs/0-1-br.pdf}
		\caption{Bayes Risk of the 0-1 loss.}
		\label{fig:0-1-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
		\centering
		\includegraphics[width=0.9\linewidth]{figs/hinge-br.pdf}
		\caption{Bayes Risk of hinge loss.}
		\label{fig:hinge-br}
	\end{minipage}
	\hfill
	\begin{minipage}{0.3\linewidth}
	\centering
	\includegraphics[width=0.9\linewidth]{figs/logistic-br.pdf}
	\caption{Bayes Risk of the logistic loss.}
	\label{fig:logistic-br}
\end{minipage}
\end{figure}

@@

    %\btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
    \jessie{Skip and go to orange for now.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$ by taking an appropriate invertible linear projection to an affine subspace $A : \reals^n_+ \to \reals^{n-1}_+$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the interior of $\simplex$.
  (For intuition, one can consider the relative interiors in $\reals^\Y_+$, but we need to consider interiors in order to apply previous results.)
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
  \raft{I believe we can remove mentions of power diagrams here; let's give it a try.  I don't think we need to project yet, given what we say next.}
  The projection of its epigraph $E_{\ell}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional (in $n-1$ dimensions) and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$. \jessiet{Don't need Theorem 1; can use Lemma~\ref{lem:finite-full-dim} instead. -21 Mar 21}

@@

\raf{Something like this:}\\
Together, Lemma~\ref{lem:loss-restrict} and Proposition~\ref{prop:embed-bayes-risks} give the following useful tool for finding embeddings.
\begin{corollary}\label{cor:representative-embeds-restriction}
  Let surrogate loss $L:\reals^d \to \reals^\Y_+$ be given.
  If a finite set $\U \subseteq \reals^d$ is representative for $L$, then $L$ embeds the discrete loss $L|_\U$.\jessie{Type check: $\reals^d$ vs $\R$?}
\end{corollary}

@@

\raft{I wonder if we should demote this to a corollary.  We can write the proof of the reverse implication in Proposition~\ref{prop:embed-bayes-risks} like this: first show that if $\risk{L}$ is polyhedral, there is a finite $\U$ which is representative for $L$.  Then show that if $\risk{\ell} = \risk{L}$ then there is some $\Sc$ that is bijective to the particular $\U$ we constructed.  I'm not sure how this will go, but perhaps worth a try, since it would avoid the proof duplication too!}
\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss $\ell : \R \to \reals^\Y_+$ if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  If $L$ embeds a discrete $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$ and polyhedral.
  For the converse, let $\risk{L}$ be polyhedral. %; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  \proposedadd{Form the finite set $\Sc := \Sc(L)$ as in Definition~\ref{cons:rep-set}.
  %For each facet of $E_L$, which is full-dimensional, there must be some interior distribution $p$ such that $p \mapsto (p, \inprod{p}{L(u)})$ uniquely supports $E_L$, and such a $u$ must exist or else the Bayes risk is not attained.  Take $\Sc$ to be the collection of such reports $u$, and observe $\Sc$ is representative for $L$.  
  By Corollary~\ref{cor:representative-embeds-restriction}, $L$ embeds $L|_\Sc$, which is finite by construction.}
%  The projection of the epigraph of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
%  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
%  Define $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
\end{proof}

@@

\begin{lemma}
	\label{lem:poly-loss-poly-risk}
	If $L$ is polyhedral, $\risk{L}$ is polyhedral.
\end{lemma}
\begin{proof}
	Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and $\Gamma = \prop{L}$.
	By Lemma~\ref{lem:polyhedral-range-gamma}, $\U = \Gamma(\simplex)$ is finite. \jessie{Do we need Lemma 3 or can we just conclude $L$ has a finite representative set without it?}
	For each $U\in \U$, select $u_U \in U$, and let $\Sc = \{u_U : U \in\U\}$.
	$\Sc$ is representative for $L$, so Lemma~\ref{lem:loss-restrict} gives us $\risk{L} = \risk{L|_{\Sc}}$, which is polyhedral as $\Sc$ is finite.
\end{proof}

@@

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
	Let $\R^*$ be a finite representative set for $L$ eliciting $\Gamma$.
	The following are equivalent:
	\begin{enumerate}
		\item[a.] $\R^*$ is a minimum representative set for $L$.
		\item[b.] $L|_{\R^*}$ is non-redundant.
		\item[c.] For all $r \in \R^*$, $\Gamma_r$ is full-dimensional and there is no $r' \in \R^*$ such that $\Gamma_{r'}= \Gamma_r$, and $\cup_{r\in\R^*} \Gamma_r = \simplex$.\jessie{Remove from here and bring back for property discussion?}
	\end{enumerate}
\end{proposition}
\begin{proof}[Sketch]
	$(a \implies b)$  
	We show the contrapositive: suppose $L|_{R^*}$ is redundant.
	Then there is a $r,r' \in \R^*$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
	Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
	Therefore, $\R^* \setminus \{r\}$ still a representative set, so $\R^*$ is not minimum.

@@

	$(c \implies a)$
	As $\Gamma_r$ is full-dimensional and there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$, for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
	Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
	Therefore, $\R$ is minimum.

	$(b \implies a)$
	Since $\R^*$ is finite, it suffices to show that for all $r \in \R^*$, there exists some $p_r \in \simplex$ such that $\{r\} = \Gamma(p_r)$.
	This implies the result, as removing $r$ from $\R^*$ would make $\Gamma(p_r) = \emptyset$, and therefore $\R^* \setminus \{r\}$ would not be representative.

	If there was an $r \in \R^*$ such that there was no such $p_r$, but $\Gamma_r \not \subseteq \Gamma_{r'}$ for any other $r' \in \R^*$, then we must have some $r', r''$ such that there exists a $p_{r'}^r$ and $p_{r''}^r$ such that $\{r,r'\} \subseteq \Gamma(p_{r'}^r)$ and $r'' \not \in p_{r'}^r$, and similarly, $\{r, r''\} \subseteq \Gamma(p_{r''}^r)$ and $r' \not \in \Gamma(p_{r''}^r)$.

	Since $r \in \Gamma(p_{r'}^r)$, we have the hyperplane $H_L(p_{r'}^r; r) := \inprod{p_{r'}^r}{L(r)}$ supporting $\risk{L}$ at $p_{r'}^r$, and similarly $H_L(p_{r''}^r; r)$ supports $\risk{L}$ at $p_{r''}^r$.
	However, $H_L(p_{r'}^r; r'')$ does not support $\risk{L}$ at $p_{r'}^r$, so we have
	\begin{align*}
	\inprod{p_{r'}^r}{L(r)} &= \inprod{p_{r'}^r}{L(r')} \neq \inprod{p_{r'}^r}{L(r'')}\\
	\inprod{p_{r''}^r}{L(r)} &= \inprod{p_{r''}^r}{L(r')} \neq \inprod{p_{r''}^r}{L(r'')}
	\end{align*}
	However, this yields a contradiction since $H_L(\cdot; r)$ is linear in its first argument, and therefore $\risk{L}$ must be linear between $p_{r'}^r$ and $p_{r''}^r$.
%	This means that each $\Gamma_r \subseteq \Gamma_{r'}$ or $\Gamma_{r''}$; in either case, we contradict non-redundancy.
%	\jessie{This is not well-written... nor correct as written?}

	$(a \implies c)$
	The level sets being full-dimensional follows from closure of level sets.
	No duplicate level sets follows from minimum representative sets, and union to the simplex follows from $\R^*$ representative.
\end{proof}

\begin{corollary}
	If $\R$ is a minimum representative set for $L$, then $L$ tightly embeds $L|_\R$.
\end{corollary}
Tightly embedding the restricted loss seems to make embedding construction slightly easier.
While $L|_\R$ is not always the target loss of interest, there should now be a \emph{bijection} from $\R$ to the target reports.
While an embedding only has to be constructed once and is considered an offline computation, its construction might be made easier

\begin{proposition}\label{prop:trim-unique}
	Suppose $\R$ and $\R'$ are minimum representative sets for the loss $L$.
	Then $\{L(r) \mid r \in \R\} = \{L(r') \mid r' \in \R'\}$.
\end{proposition}
\begin{proof}[Sketch]
	It suffices to show $\{L(r) \mid r \in \R\} \subseteq \{L(r') \mid r' \in \R'\}$, and equality will follow by symmetry.
	Consider $r\in \R$, and we want to show $L(r) \in \{L(r') \mid r' \in \R'\}$.
	Since $\R$ and $\R'$ are minimum representative sets, all the level sets must be full-dimensional, and therefore have well-defined interiors (Proposition~\ref{prop:tfae-min-rep-nonredundant}).
	In particular, we must have $\Gamma_r = \Gamma_{r'}$ for some $r' \in \R'$.
	If $L(r) \neq L(r')$, then there would be a distribution $p \in \inter{\Gamma_r}$ such that $\inprod{p}{L(r)} \neq \inprod{p}{L(r')}$. \jessiet{This needs more detail}
	If $\inprod{p}{L(r)} > \inprod{p}{L(r')}$, then $r' \not \in \Gamma(p)$, and $\R'$ is therefore not a representative set.
	Similarly, if the inequality were flipped, we would contradict $\R$ being a representative set.
	Therefore, we must have the losses equal, and $L(r) \in \{L(r') \mid r' \in \R'\}$.
\end{proof}

\begin{definition}[Trim]\label{def:trim-loss}
	Given a loss $L:\R \to \reals_+^\Y$, we define $\trim(L) = \{L(r) \mid r \in \R'\}$ given any minimum representative set $\R'$ for $L$.
\end{definition}

\begin{proposition}\label{prop:trim-loss-condition}
	Given an loss $L : \R \to \reals^\Y_+$, we have $\trim(L) = \{L(u) \mid u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\end{proposition}
\begin{proof}[Sketch]
	Let $\U := \{u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.

	We have $\U$ representative since for any $r \in \R \setminus \U$, we must have $\Gamma_r \subsetneq \Gamma_{r'}$ for some other $r'$, and $r' \in \U$ by partial orderings of subsets, so $\Gamma(p) \cap \U$ is never empty.

	Take any $\U' \subseteq \U$ that is a minimum representative set by pruning redundant reports from $\U$ (unique up to a choice of which duplicate report you want to keep).
	If $\{L(u) \mid u \in \U\} = \{L(u) \mid u \in \U'\}$, the result follows as a corollary of Proposition~\ref{prop:tfae-min-rep-nonredundant}.

	Clearly, $\{L(u) \mid u \in \U\} \supseteq \{L(u) \mid u \in \U'\}$, so we just need to show $\{L(u) \mid u \in \U\} \subseteq \{L(u) \mid u \in \U'\}$.
	If for $u \in \U$, we want to show there is some $u' \in \U'$ such that $L(u) = L(u')$, and the result follows.
	If $u \not \in \U'$, it must be because there is a $u' \in \U'$ such that $\Gamma_{u'} = \Gamma_u$. \jessie{Hand waving}
	These level sets are full-dimensional by Proposiiton~\ref{prop:tfae-min-rep-nonredundant}, so we must have equality of losses since there is some $p \in \inter{\Gamma_u}$ of full support, so the losses must match as the supporting hyperplane of $\risk{L}$ at $p$ is unique.
	%Since $\Gamma_u = \Gamma_{u'} \iff L(u) = L(u')$, the losses, and therefore the sets are equal.

%commented out 03 May 21	
%	Suppose $L(u) \in \trim(L)$.
%	By Proposition~\ref{prop:tfae-min-rep-nonredundant}, we know $\Gamma_u$ is a full-dimensional level set, and there exists a $p_u$ such that $\{u\} = \Gamma(p_u)$.
%	Therefore, $\Gamma_u$ cannot be a subset of any other level set, so $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
%	
%	Now, suppose $L(u) \in \{L(u) \mid \neg \exists u' s.t. \, \Gamma_u \subsetneq \Gamma_{u'}\}$.
%	If $L(u) \not \in \trim(L)$, then there is a $u'$ so that $L(u') \in \trim(L)$ and $\Gamma_u \subseteq \Gamma_{u'}$.
%	By the set construction, we must have $\Gamma_u = \Gamma_{u'}$, and since $\R$ is a minimum representative set, we know there is a $p_{u'}$ such that $\{u'\} = \Gamma(p_{u'})$.
%	Therefore, we must have $u=u'$, so $L(u') = L(u) \in \trim(L)$.
\end{proof}

\begin{proposition}\label{prop:embed-iff-trims-equal}
	Let the discrete loss $\ell$ be given.
	$L$ embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
\end{proposition}
Suppose $\gamma := \prop{\ell}$ and $\Gamma := \prop{L}$, and $\R$ a minimum representative set for $\ell$.
\begin{proof}[Sketch]
	$\implies$
	The optimality condition of embedding means $\Gamma_{\varphi(r)} = \gamma_r$ for all $r \in \R$.
	$\R$ a minimum representative set for $\ell$ then implies $\varphi(\R)$ is a minimum representative set for $L$.
	By Proposition~\ref{prop:trim-unique}, we have
	\begin{equation*}
	\trim(L) = \trim(L|_{\varphi(\R)}) = \trim(\ell|_\R) = \trim(\ell)~.~
	\end{equation*}
	The outside equalities follow from the sets being minimum representative sets, and the middle one follows from the embedding definition since losses have to match at embedded points.

	$\impliedby$
	First, take $\varphi: r \mapsto u$ if $\ell(r) = L(u)$.
	As these losses match we trivially have the second embedding condition matching losses.
	It just remains to show $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	\begin{align*}
	r \in \argmin_u \inprod{p}{\ell(u)} &\iff \ell(r) = \min_{u \in \R} \inprod{p}{\ell(u)} \\
	&\iff L(\varphi(r)) = \min_{u \in \varphi(\R)} \inprod{p}{L(u)} \\
    &\iff L(\varphi(r)) = \min_u \inprod{p}{L(u)} \\
    &\iff \varphi(r) \in \argmin_{u} \inprod{p}{L(u)}
	\end{align*}
\end{proof}

As we define one loss embedding another, one can imagine an analagous definition where one property embeds another, and we can define $\trim(\Gamma)$ as the set of level sets generated by a minimum representative set.
Even when using the language of properties, similar results to those above hold; for intuition, the level sets of a property correspond to the subgradients of the Bayes Risk of the loss eliciting it.
Since embedding also means matching Bayes Risks, the $\trim$s matching follows since the subgradients also trivially match.

\jessie{Just took old TFAE for now, but this is quite different from Prop 4, united by (c) in each}
\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto \R$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R'$.
		\item \jessie{Adding} $\R^*$ is a finite (minimum?) representative set for $\Gamma$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	Moreover, when any of the above hold, $\trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
